\huge A Usability Evaluation of Tor Launcher

### 2016-10-28 pets2017-paper/pets2017-paper.tex
introduce NEW and OLD

\subsection{Results} 
124 people participated in our experiment, but we used data from 114. We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface. Table~\ref{table:participant-summary} gives an overview of the results, summarizing completion rate, connection time, and configuration time by condition. Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.

>>>>

\subsection{Results} 
124 people participated in our experiment, but we used data from 114. We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface. In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}). Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.
